Predicting FOMC Actions using NLP; Assesing the impact of matrix sparsity and regularization

### 2019-05-13 presentation/paperv2.tex
v2

\section{Objective}
\begin{enumerate}
\item Since its pretty easy to just blindly apply tools to a set of data we wanted to understand the 
characteristics of the output from the text processing functions (in our case CountVectorizer) in terms of number of features, matrix sparsity, matrix norm
that are generated from calls to this function.
\item Assess the effeiveness of Bayesian Approaches and Regularization on the analysis.
\item Determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate).
\item Because 70$\%$ of the actions are ``no action'', make sure the prediction is not always just ``no action'' (which would give a 70$\%$ accuracy).
\end{enumerate}

@@

>>>>

\section{Objective}
\begin{enumerate}
\item Since its pretty easy to just blindly apply tools to a set of data we wanted to understand the 
characteristics of the output from the text processing functions (in our case CountVectorizer) in terms of number of features, matrix sparsity, matrix norm
that are generated from calls to this function.
\item Assess the effeiveness of Multinomial Niave Bayes and Logistic Lasso applied to problmes where the feature size is orders of magnitues larger than the label size.
\item Determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate).
\item Because 70$\%$ of the actions are ``no action'', make sure the prediction is not always just ``no action'' (which would give a 70$\%$ accuracy).
\end{enumerate}

@@

\subsubsection{Training, Testing and Determining the efficacy of the Models}
For this study we randomly sample 75$\%$ of the corpus for training and then 
predict Fed action using the ramining 25$\%$ of the data and calculate
\begin{itemize}
\item Accuracy
\item Precision
\item Recall
\item F1 Score
\end{itemize}
Approximately 70$\%$ of the time there is no Action so a model that does nothing will
have an accuracy of 70$\%$, but a recall of 0.  The results are summarized using F1
score.
